### 2024-03-25 doc/sections/mav-semantics.tex
[ tex ] some todos and comments
[ tex ] more semantics

@@

\begin{definition}
  A \emph{$*$-autonomous partial order} is ... TODO

\end{definition}

\begin{remark}
  The structure of a $*$-autonomous partial order has a number of
  immediate consequences, but we leave description of these until
  after the definition of MAV algebra below. \bob{because there are
    even more consequences in the presence of additive and duoidal
    structure}
\end{remark}

FIXME: cite that combinatorics book.
\begin{definition}
  Two pomonoids $(\bullet, i)$ and $(\rhd, j)$ on a partial order
  $(A, \leq)$ are in a \emph{duoidal} relationship if the following
  inequalities hold:
  \begin{enumerate}
  \item $(w \rhd x) \bullet (y \rhd z) \leq (w \bullet y) \rhd (x \bullet z)$
  \item $j \bullet j \leq j$
  \item $i \leq i \rhd i$
  \item $i \leq j$
  \end{enumerate}
\end{definition}

@@

@@

\begin{proposition}\label{prop:mav-algebra-consequences}
  \bob{Consequences of the definition, as listed in the Agda}
\end{proposition}

\begin{definition}\label{defn:mav-interpretation}
  Let $\mathit{At}$ be a set of atomic propositions. Given an
  MAV-algebra $(A, \leq, \otimes, \rhd, I, \lnot)$ and valuation
  $V : \mathit{At} \to A$, define the interpretation of MAV Formulas
  as follows:
  \begin{mathpar}
    FIXME
  \end{mathpar}
\end{definition}

\begin{theorem}\label{thm:soundness}
  The interpretation defined in Definition
  \ref{defn:mav-interpretation} is sound: for all formulas $P$, if
  $P \longrightarrow^* I$, then $I \leq \llbracket P \rrbracket$.
\end{theorem}

@@

\newcommand{\LowerSet}[1]{\widehat{#1}}
\newcommand{\Day}[1]{\mathop{\widehat{#1}}}

@@

\subsubsection{Lower Sets}

@@

\newcommand{\ClosedLowerSet}[1]{\widehat{#1}^+}
\newcommand{\ClosedDay}[1]{\mathop{\widehat{#1}^+}}
\newcommand{\Chu}{\mathrm{Chu}}
\newcommand{\op}{\mathrm{op}}

@@

>>>>

\newcommand{\LowerSet}[1]{\widehat{#1}}
\newcommand{\Day}[1]{\mathop{\widehat{#1}}}
\newcommand{\ClosedLowerSet}[1]{\widehat{#1}^+}
\newcommand{\ClosedDay}[1]{\mathop{\widehat{#1}^+}}
\newcommand{\Chu}{\mathrm{Chu}}
\newcommand{\op}{\mathrm{op}}

@@

\begin{definition}
  A \emph{$*$-autonomous partial order} is a structure
  $(A, \leq, \otimes, I, \lnot)$ where $(\otimes, I)$ is a pomonoid on
  $(A, \leq)$ and $\lnot : A^\op \to A$ is an anti-monotone and
  involutive operator on $A$, together satisfying
  $x \otimes y \leq \lnot z$ iff $x \leq \lnot (y \otimes z)$.  A
  $*$-autonomous partial order satisfies \emph{mix} if $\lnot I = I$.
\end{definition}

\begin{remark}
  The structure of a $*$-autonomous partial order has a number of
  immediate consequences, but we leave description of these until
  after the definition of MAV-algebra below. \bob{because there are
    even more consequences in the presence of additive and duoidal
    structure}
\end{remark}

FIXME: cite that combinatorics book.

\begin{definition}
  Two pomonoids $(\bullet, i)$ and $(\rhd, j)$ on a partial order
  $(A, \leq)$ are in a \emph{duoidal} relationship if the following
  inequalities hold:
  \begin{enumerate}
  \item $(w \rhd x) \bullet (y \rhd z) \leq (w \bullet y) \rhd (x \bullet z)$
  \item $j \bullet j \leq j$
  \item $i \leq i \rhd i$
  \item $i \leq j$
  \end{enumerate}
\end{definition}

@@

\begin{remark}
  If $\bullet$ is a join, or $\rhd$ is a meet, then all the conditions
  for a duoidal relationship are automatically met for any other
  monoid. \bob{fwd ref to where we use this.}
\end{remark}

\begin{remark}
  The duoidal relationship is not symmetric.
\end{remark}

@@

\begin{proposition}\label{prop:mav-algebra-consequences}
  Let $(A, \leq, \otimes, ;, I, \lnot)$ be a MAV-algebra.
  \begin{enumerate}
  \item There is another pomonoid structure $(\parr, I)$ on
    $(A, \leq)$, defined as
    $x \parr y = \lnot(\lnot x \otimes \lnot y)$.
  \item $(\otimes, I)$ and $(\parr, I)$ are linearly distributive
    \cite{cockett}:
    $x \otimes (y \parr z) \leq (x \otimes y) \parr z$.
  \item $(A, \leq)$ has binary joins, given by
    $x \oplus y = \lnot (\lnot x \with \lnot y)$.
  \item $\oplus$ distributes over $\otimes$:
    $x \otimes (y \oplus z) = ((x \otimes y) \oplus (x \otimes z)$.
  \item $\with$ distributes over $\parr$:
    $(x \parr z) \with (y \parr z) = (x \with y) \parr z$.
  \item $;$ is entropic over $\parr$:
    $(w \parr x); (y \parr z) \leq (w;y) \parr (x;z)$.
  \item $;$ is entropic over $\with$:
    $(w \with x); (y \with z) \leq (w ; y) \with (x; z)$.
  \item $\oplus$ is entropic over $;$:
    $(w ; x) \oplus (y ; z) \leq (x \oplus y) ; (x \oplus z)$.
  \end{enumerate}
\end{proposition}

\newcommand{\sem}[1]{\llbracket #1 \rrbracket}

\begin{definition}\label{defn:mav-interpretation}
  Let $\mathit{At}$ be a set of atomic propositions. Given an
  MAV-algebra $(A, \leq, \otimes, \rhd, I, \lnot)$ and valuation
  $V : \mathit{At} \to A$, define the interpretation of MAV Formulas
  as follows: $\sem{\vUnit} = I$, $\sem{a} = V(a)$,
  $\sem{\vDual a} = \lnot V(a)$,
  $\sem{\vP\vTens\vQ} = \sem{\vP} \otimes \sem{\vQ}$,
  $\sem{\vP\vParr\vQ} = \sem{\vP} \parr \sem{\vQ}$,
  $\sem{\vP\vSeq\vQ} = \sem{\vP};\sem{\vQ}$,
  $\sem{\vP\vWith\vQ} = \sem{\vP} \with \sem{\vQ}$, and
  $\sem{\vP\vPlus\vQ} = \sem{\vP} \oplus \sem{\vQ}$.
\end{definition}

\begin{lemma}
  For all $\vP$, $\sem{\vDual{\vP}} = \lnot \sem{\vP}$.
\end{lemma}

\begin{theorem}\label{thm:soundness}
  The interpretation defined in Definition
  \ref{defn:mav-interpretation} is sound: for all formulas $P$, if
  $P \longrightarrow^* I$, then $I \leq \sem{P}$.
\end{theorem}

@@

@@

\subsubsection{Lower Sets and Day pomonoids}

@@

@@

\begin{lemma}
  \bob{entropy on residuals}
\end{lemma}
